An Audio-Based 3D Spatial Guidance AR System for Blind Users\thanks{JMC, BB and HS were supported by NIH grant 5R01EY025332 and NIDILRR grant 90RE5024-01-00. We thank Dr. Roberto Manduchi, Dr. Natela Shanidze, Dr. Santani Teng and Dr. Ali Cheraghi for helpful suggestions about the experiments.}

### 2020-06-10 manuscript.tex

%%TODO: figure description
%%TODO: split the 4 figures ?
\begin{figure}
\includegraphics[width=5.5cm, height=4.1cm,]{res/img/histNG.png}
\includegraphics[width=6.5cm, keepaspectratio,]{res/img/lines.png}
\includegraphics[width=5.5cm, keepaspectratio,]{res/img/fig2a.jpg}
\includegraphics[width=6.5cm, keepaspectratio,]{res/img/fig2b.jpg}
\caption{
(Upper-left) Histogram of the times to find the hotspots per guidance condition. 
(Upper-right) Line plot showing the average time to find the hotspot ($\pm{ SE}$) per subject and per guidance condition. 
(Bottom-left) Time to find target hotspot location for G (‘o’ symbol) vs. NG  (‘x’ symbol) conditions. The times for each of the 10 hotspots are shown, for each participant (indicated on the y axis and also using color). 
(Bottom-right) Histogram of the differences (paired by hotspot) in time to find the hotspot.}
\label{fig:res}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=6cm, keepaspectratio,]{res/img/hist1.png}
\includegraphics[width=6cm, keepaspectratio,]{res/img/lines.png}
\includegraphics[width=6cm, keepaspectratio,]{res/img/hist_diff.png}
\includegraphics[width=6cm, keepaspectratio,]{res/img/full.png}
\caption{
\emph{(Upper-left)} Histogram of the times to find the hotspots per guidance condition. 
\emph{(Upper-right)} Line plot showing the average time to find the hotspot ($\pm{ SE}$) per subject and per guidance condition. 
\emph{(Bottom-left)} Histogram of the differences (paired by hotspot) in time to find the hotspot.
\emph{(Bottom-right)} Time to find target hotspot location for each participant, colored by guidance mode.}
\label{fig:res}
\end{figure}
